Appendix

### 2025-04-14 manuscript/appendix.qmd
fix outputs of study_info and appendix

---
title: Appendix
aliases:
  - /appendix.html
format: 
  html: 
    echo: true
    code-fold: show
    output-file: appendix-code.html
    wordcount-banner: true
    theme: 
      - zephyr
      - ../assets/custom.scss
    toc: true
    shift-heading-level-by: 1
    code-summary: "Show the code"
    title-block-banner: "#000D51"
    include-in-header:
        - text: |
            <style type="text/css">
            h2.hide {
                display: none;
            }
            </style>
  wordcount-html: 
    output-file: appendix.html
    wordcount-banner: true
    echo: false
    theme: 
        - zephyr
        - ../assets/custom.scss
    toc: true
    shift-heading-level-by: 1
    title-block-banner: "#000D51"
    include-in-header:
        - text: |
            <style type="text/css">
            h2.hide {
                display: none;
            }
            </style>
  docx: default
  #hikmah-manuscript-docx: default
  hugo-md:
    include: false
    echo: false
    html-math-method: mathjax
    output-file: appendix_hugo.md
    suppress-bibliography: false
  gfm:
    echo: true
    output-file: appendix_gfm.md
    suppress-bibliography: true
  hikmah-manuscript-pdf:
    output-file: rs_appendix.pdf
    echo: false
    mainfont: "Linux Libertine O"
    mainfontoptions:
    - "Numbers=Proportional"
    - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
    knitr:
        opts_chunk:
            dev: "cairo_pdf"
format-links:   
    - text: HTML
      href: appendix.html
      icon: file-minus
    - text: HTML (with code)
      href: appendix-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      href: rs_appendix.pdf
      text: PDF version
      icon: file-pdf
    - docx
    - gfm

@@

@tbl-s2-prop shows that, once again, participants in the kWh condition achieved closer alignment with the target goals (44% exact matches), followed by Percentage (27%) and USD (18%). These percentages are consistent with the patterns observed in Study 1, reinforcing the conclusion that providing goals in kWh supports better accuracy.

@@

@@

As in Experiment 1, we further investigated the role of individual differences in energy literacy in predicting planning accuracy. A Bayesian linear regression model, analogous to the one used in Experiment 1 (log_abs_error ~ els + (1|id) + (1|state)), revealed a significant negative relationship between energy literacy scores and log-transformed absolute error (Estimate = -3.21, 95% CI: -3.89 to -2.52). This finding indicates that participants with higher energy literacy scores tended to produce more accurate plans, exhibiting smaller deviations from the target reduction goals. The conditional effect plot (@fig-s2-els) visually confirms this relationship, showing a clear decreasing trend in log absolute error as energy literacy increases.

>>>>

---
title: Appendix
aliases:
  - /appendix.html
format: 
  html: 
    echo: true
    code-fold: show
    output-file: appendix-code.html
    wordcount-banner: true
    theme: 
      - zephyr
      - ../assets/custom.scss
    toc: true
    shift-heading-level-by: 1
    code-summary: "Show the code"
    title-block-banner: "#000D51"
    include-in-header:
        - text: |
            <style type="text/css">
            h2.hide {
                display: none;
            }
            </style>
  # wordcount-html: 
  #   output-file: appendix.html
  #   wordcount-banner: true
  #   echo: false
  #   theme: 
  #       - zephyr
  #       - ../assets/custom.scss
  #   toc: true
  #   shift-heading-level-by: 1
  #   title-block-banner: "#000D51"
  #   include-in-header:
  #       - text: |
  #           <style type="text/css">
  #           h2.hide {
  #               display: none;
  #           }
  #           </style>
  docx: default
  #hikmah-manuscript-docx: default
  hugo-md:
    include: false
    echo: false
    html-math-method: mathjax
    output-file: appendix_hugo.md
    suppress-bibliography: false
  gfm:
    echo: true
    output-file: appendix_gfm.md
    suppress-bibliography: true
  # hikmah-manuscript-pdf:
  #   output-file: rs_appendix.pdf
  #   echo: false
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #   - "Numbers=Proportional"
  #   - "Numbers=OldStyle"
  #   mathfont: "Libertinus Math"
  #   knitr:
  #       opts_chunk:
  #           dev: "cairo_pdf"
  apaquarto-pdf: 
    toc: false
    echo: false
    #output-file: rs_apa_code.pdf
    output-file: rs_appendix.pdf
   # floatsintext: true
format-links:   
    - text: HTML
      href: appendix.html
      icon: file-minus
    - text: HTML (with code)
      href: appendix-code.html
      icon: file-plus
    - format: hikmah-manuscript-pdf
      href: rs_appendix.pdf
      text: PDF version
      icon: file-pdf
    - docx
    - gfm

@@

<!-- @tbl-s2-prop  -->

shows that, once again, participants in the kWh condition achieved closer alignment with the target goals (44% exact matches), followed by Percentage (27%) and USD (18%). These percentages are consistent with the patterns observed in Study 1, reinforcing the conclusion that providing goals in kWh supports better accuracy.

@@

```{r}
#| eval: false

@@

As in Experiment 1, we further investigated the role of individual differences in energy literacy in predicting planning accuracy. A Bayesian linear regression model, analogous to the one used in Experiment 1 (log_abs_error ~ els + (1|id) + (1|state)), revealed a significant negative relationship between energy literacy scores and log-transformed absolute error (Estimate = -3.21, 95% CI: -3.89 to -2.52). This finding indicates that participants with higher energy literacy scores tended to produce more accurate plans, exhibiting smaller deviations from the target reduction goals. The conditional effect plot (fig-s2-els) visually confirms this relationship, showing a clear decreasing trend in log absolute error as energy literacy increases.
